---
title: "manipulating dataframe techiniques"
output:
  html_document:
    df_print: paged
  pdf_document: default
---


#Subset(dataframe, select =c( ) )

We can take the example of airquality dataframe and manipulate on it.
```{r}
l<-airquality
subset(l,select = Ozone:Temp)
subset(l,select = c(Solar.R,Day))
subset(l,Ozone>40,select = -Month) #- means remove this column
subset(l,l$Ozone>30) #This can be used if the column name has multiple words, and then we use
subset(l,l$Month==7) #We must use == as a conditional syntax
```

#arrange( ) / order( )

arrange function take the default settting of ascending order, and we can enter multiples variable with the first variables being arranged first and as follows. **arrange** is essensially the dataframe version of **order**.

```{r}
library(plyr)
arrange(l,Ozone,Wind) #If Ozone are the same, the function then compare Wind value.
arrange(l,Ozone,Day,na.last=TRUE, decreasing = TRUE) #The default value for decreasing is FALSE, and na.last = TRUE is the default value.Please use ?arrange for further information. 

order(l$Ozone)
```
#Remove NA 

We must know that sometimes NA in the dataframe are shown as "Not Available" or other strings which are insane, and R cannot detect them as NA but as a string "Not Available"(if "Not Available" is the case). We need to use function **na.strings = "Not Available"**(or something else) to let R know that these strings mean NA. So in the next step we can use function such as **na.omit( an R object, typically a data fram), dataframes[complete.cases(dataframes),]** to eliminate the rows that contains NA.
```{r}

df<-data.frame("weather"=c("Sunny","Humid","Cold","Cool","Cloudy","Not Available",NA), "Index" = c(1,3,4,2,1,11,4))
df
na.omit(df)
Dataframes<-read.csv("outcome-of-care-measures.csv",na.strings = "Not Available",stringsAsFactors = FALSE) #Don't convert string to factors because factors have levels and the same factors as viewed at the same level
dataframes<-Dataframes[,c(2,7,11,17,23)]
dataframes
dataframes[complete.cases(dataframes),] #It is the same as na.omit(dataframes)
```


