---
title: "Swirl"
author: "Qizhe Cui"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

we can use **identical(a,b)** funciton to compare if two objects are the same  


If we want to assign a dataframe with column name then we use **colnames(my_data)<-cnames**
where cnames is a concatenation of names

If we want to know all the objects in my workspace, sue **ls()**. If we want to know all the files in my working directory, use **dir()**  
we can also create a directory in the current working directory by **dir.create()** and we can use **list.files()**to check all the files in our working directory, then we can use **file.create()** to create a file. If we want to rename a file, we can use **file.rename(from, to)**. In order to know the path of a file, we use **file.path()**.


# Sequence

We can use the function **seq(1,20,0.5)** for all number from 1 to 20 with interval 0.5 and we can use **seq(1,20,length=20)** for 20 number equally distributed from 1 to 20. If we want to replicate a number for 40 times, then we use **rep(0, times = 40)**. This also applies to vector and examples are **rep(c(1,2,3), times = 20)** or we want each number to repeat several times.
```{r}
a<-rep(c(1,3,5),times=10)
b<-rep(c(1,2,3), each =10)

a
b

```

# Subsetting 

In order to apply more than one condicition on a dataframe/list, we use the symbol &

```{r}
x <- list(NA,0.32,NA,-2.12,2.3,1.23,NA)
a<-x[is.na(x) & x>0]
a
```
If we want to omit specific element of a list we can use miuns sign
```{r}
x <- rnorm(20)
x[c(-2:-10)]#This omits the 2nd to 10st elements 
x [-c(3,4,6)]#We can put the minus sign in front
```

if we want to remove all the variales in rstudio we first use  **rm(list=ls())** where **ls()** give us all the variables in the rstudio.