---
title: "Week 4"
output:
  html_document:
    df_print: paged
---
# The str function

It displays compactly the contents of a R obejct (Note that function is also a R obejct). Str can give you a quick examination
```{r}
str(list(1,2,x="3",TRUE))
library(datasets)
l<-airquality
str(head(l)) #The structure of the first 6 rows of l

m<-matrix(rnorm(24),3,8)
str(m)

str(split(l,l$Month)) #The structure of the list which is based on different months of the airquality
```

# Simulation for statistics

**rnorm** function can simulate a normal distribution with given mean and SD. Probability generating function have four functions asscociated with them, which are **d for density, r for random number generation, p for cumulative distribution, and q for quantile function**  If we want to reproduce the random number that we generate then we use **set.seed( )** function.

```{r}
set.seed(1)
rnorm(10)
set.seed(2)
rnorm(10)
set.seed(1)
rnorm(10)
set.seed(2)
rnorm(10)
```
Note that d,r,p,q are prefix for any distribution types such as poisson, bionomial, geometric. The p and q are reverse and p represent the total area under the graph whereas q is the corresponding value. 
```{r}
rpois(10,5) 
ppois(7,3)  #return the culmulative area at the first 7 trails when the mean is 3, 
qpois(0.98,3) #return the number you need to get a 98% culmulative area
dbinom(3,6,0.5) #return the probability of getting a 3  when the total is 6 and probability is 0.5

```

#Generating random number from a generalised linear model

Suppose that we have a relationship between y and x and we want to simulate the result of y, then we can plot the graph and visulize their relationship.
```{r}
set.seed(1)
x<-rnorm(100)
e<-rnorm(100,1,2)
y<- 2+ 0.5 * x +e
summary(y)
plot(x,y)
```
```{r}
# If we want to create a binary distribution which is in fact a binomial distribution then we can

x<-rbinom(100,1,0.5)
y<-2 + 0.5 *x +e
summary(y)
plot(x,y)

# if we want some complciated relationship involving log function. We can suppose y ~ Po(mu)

x<-rnorm(100)
log.mu<-2+0.5 * x
y<-rpois(100,exp(log.mu))
summary(y)
plot(x,y)





```


# Random sampling 

we use the **sample** function to draw randomly from a specific set of scalar R objects such as number and letters. If we don't specify the trails, then it will return a permutation of the set of number.
```{r}
sample(2:12)
sample(2:12,replace = TRUE) #replace= TRUE means that they can repeat 
sample(1:10,5)
sample(letters,3)
sample(c(0,1,2),100,replace=TRUE,prob = c(0.2,0.3,0.5))
```


# R Profiler system.time() R分析器

The function **system.time( )** can return the amount of time taken to evaluate the expression. The class of the returned object is **proc_time**. The **user time** is the time that CPU takes for this expression, the **elapsed time** is the time that I experience. Instances of elapsed time > user time includes reading from a web page because the computer wait for the network rather than running the program itself. 
```{r}
system.time({
  n<-1000
  r<-numeric(n) #Note that numeric(n) create a vector of 0 of length n
  for (i in 1:n){
    x<-rnorm(n)
    r[i]<-mean(x)
  }
})
system.time(readLines("https://dictionary.cambridge.org/"))  
```


# R Profiler Rprof(), summaryRprof
Rprof() function takes a default interval of 0.02 seconds. It repeats if running the program takes over 0.02 second. We use the **summaryRrof()** function to tabulate the outputs of R profiler. There are two methods for normalizing the data, "by.total" and "by.self". **by.total** calculates the time spent both in top levels and low levels function whereas **by.self** only calculates the time spent in the top levels function


#Swirl-looking at data

If we want to know how much space a R object(such as dataframe) takes we can use the function **object.size()**, and **names()** will return the names of the columns in the dataframe. Also the **str()** helps us to understand the structure of a R object

#Swirl simulation

If we want to replicate a distribution n times then we can use the replicate function **replicate() ** , which creates a matrix with each columns representing the single group result. If we want to know the mean of each groups , we can use **colMeans()**.
```{r}
a<-replicate(100,rpois(5,10))
cm<-colMeans(a)
hist(a) #The histogram looks like a normal distribution because of the central limit theorem 

```

# Swirl basic graphics
plot function has many arguments such as **main, sub, xlim,ylim, xlab,ylab**. For more plz type ?plot.  We can also use **boxplot()** to plot graph simply use xx ~ xx with data = xx. The function **hist()** can plot a single variable 
```{r}
boxplot(mpg~cyl,data = mtcars)
```
