---
title: "Week 2"
author: "Qizhe Cui"
date: "29/07/2020"
output: html_document
---

A usually used method in for loop is **seq_len()** where the argument is a positive integer and we use the method to iterate every number of the range.
```{r}
x<- matrix(1:9,3,3)
for (i in seq_len(nrow(x))){
  for (j in seq_len(ncol(x))){
    print(x[i,j])}}
x
```

# While loop and multiple conditions

If we want to apply multiple conditions in a loop we can use the symbol **&&** and here is an example 
```{r}
z<-5
while (z >=3 && z<=10){
  print (z)
  coin<-rbinom(1,1,0.5)
  if (coin ==1){
    z<- z+1
    
  }else{
    z<-z-1
    
  }
}
```
# Repeat and break

Repeat is a loop method that keep running until the break condition is met, which is similar to while loop. 
```{r}
x<-0
a<-10
repeat{
  print (identical(x,a))
  if(x>=a){
    break
  }else{
    x<-x+1
  }
}
```
# Next

Next method is used to skip some unnessary iteration for example we don't want the first 20 iteration which is a waste of time or will dirupt the result.
```{r}
for (i in seq(1,100,length=9)){
  if (i<=20){
    next
  }
  print (i)
}

```
# Function
function in R is demonstrated below. Note that numeric (n) return a sequence of 0 with length(n)
```{r}
columnmeans<-function(x){
  col<-ncol(x)
  means<-numeric(col)
  for (i in 1:col){
    means[i]<-mean(x[,i],na.rm = TRUE)
  
    
  }
  means
}
columnmeans(airquality)

```
# How to convert string into date/time

We can access the current time using **Sys.time()** function and the time can be formatted with funciton **POSIXct()** or **POSIXlt()**. The default setting is "%Y-%m-%d %H:%M:%S", but we can convert string in different format into the default format by **strptime**
```{r}
x<-Sys.time()
as.POSIXct(x)
a<-"2020, September 20, 10:20:23"
b<-strptime(a,"%Y, %B %d, %H:%M:%S") #Note that we use %B to denote month and %M for minutes
b
class(b)







```

In order to compare two dates/time in different format, we need to use **as.()** function
```{r}
x<-as.Date("2012-10-12")
y<-strptime("2012 January 10, 10:55:55", "%Y %B %d, %H:%M:%S")
x<-as.POSIXlt(x)
y-x

a<- as.Date(y)
b<-as.Date(x)
a-b


#If we want to get a date string, we can use
h<-as.Date("January 10 2012", "%B %d %Y")
h
l<-as.Date("2012-10-19")
l
```
# Logic

The basic logic operation includes &, &&, |, ||, !, xor(), identical( , ), isTRUE(). We also should remember that the && operation is executed after the ||.
If we want are given a vector of number and want to know the indice of its elements which are greater than 7 then we can use the **which** function 
```{r}
x<-sample(10)
x
which(x>=7)
FALSE && 6 >= 6 || 7 >= 8 || 50 <= 49.5
```
 Tje **any** function is TRUE if any elements in it are TRUE and the **all** function is TRUE only if all elements in it are TRUE.
```{r}
any(sample(10)<0)
all(sample(4)>=1)
```
 

# Function

In defining a function, one strict rule is that all arguments that come after ··· must have default value  

# Binary operation
We can write binary function which take left and right input with special simbol %xx%, example are as below
```{r} 
"%squre_then_plus_one%"<-function(a,b){
  (a ^ 2) * (b ^ 2) +1
}
3 %squre_then_plus_one% 2

```

# ... operation

In order to denote the nth element in a ... expression, we need to use another variable to denote ... as a list and then subset it.
```{r}
mad_libs<-function(...){
  args<-list(...)
  person<-args[["person"]]
  time<-args[["time"]]
  place<-args[["place"]]
  paste(person,"commited homicide","in",place,"at",time)
}
mad_libs(person="Qizhe",time="morning",place="schools")
```
